---
title: "ST5218_Finance_Tut_1"
author: 
- Zhu Xu
- User ID:E0337988
- Matriculation ID:A0191344H
date: "2019/1/28"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Question_1:

From Yahoo finance, download the adjusted price of Stock of Boeing (symbol in New York stock exchange Market: BA) from Jan. 1, 2001 to Dec. 30, 2010.

(a) Draw the daily prices

```{r}
library(tseries)
library(forecast)
library(zoo)
price_BA = get.hist.quote(instrument = "T",
                   start = "2001-01-01", end = "2010-12-30",
                   quote = c("AdjClose"),provider = "yahoo",
                   compress = "d")
plot(price_BA)
```

(b) Draw the daily net returns
```{r}
log_return_BA = diff(log(price_BA))
net_return_BA = exp(log_return_BA)-1
plot(net_return_BA)
```
\newpage
(c) Draw the daily log returns
```{r}
plot(log_return_BA)
```

###Question_2:

Suppose closed price of a stock is $ 123.

(a) If the net return in the next 5 days are respectively 0.01, -0.01, 0.02, -0.02, and 0, what is the price of the stock at the end of the 5th day?

p_5th $= 123\times (1+0.01)\times (1-0.01)\times (1+0.02)\times (1-0.02)\times 1 =$ $ 122.9385.

(b) If the log return in the next 5 days are respectively 0.01, -0.01, 0.02, -0.02, and 0, what is the price of the stock at the end of the 5th day?

p_5th $= 123\times e^{0.01}\times e^{-0.01}\times e^{0.02}\times e^{-0.02}\times 1 =$ $ 123.


(c) If the net return in the next 5 days are respectively 0.01, -0.01, 0.02, -0.02, and 0, find their respective log returns?

Since $r_t =log(1+R_t)$,

Thus, $r_{t1}=log(1+0.01),\quad r_{t2}=log(1-0.01),\quad r_{t3}=log(1+0.02),\quad r_{t4}=log(1-0.02),\quad r_{t5}=0$

###Quetion_3:

###Quetion_4:

$33.49,33.4,33.5,33.17$

$33.6*(1-\frac{0.49}{33.6}),33.55*(1-\frac{0.49}{33.6}),34.66*(1-\frac{0.49}{33.6}),35.15*(1-\frac{0.49}{33.6})$

$35.33*(1-\frac{0.46}{35.33})*(1-\frac{0.49}{33.6}),35.49*(1-\frac{0.46}{35.33})*(1-\frac{0.49}{33.6}),35.65*(1-\frac{0.46}{35.33})*(1-\frac{0.49}{33.6}),35.56*(1-\frac{0.46}{35.33})*(1-\frac{0.49}{33.6})$

$36.02*(1-\frac{0.46}{36.02})*(1-\frac{0.46}{35.33})*(1-\frac{0.49}{33.6}),35.84*(1-\frac{0.46}{36.02})*(1-\frac{0.46}{35.33})*(1-\frac{0.49}{33.6})$

###Quetion_5:

a)

$log(\frac{P_1}{P_0})=r_1\sim N(0.001,0.0015^2))$

$P(P_1<990)=P(r_1<log(\frac{990}{1000}))=0.23\qquad R:pnorm(log(0.99),0.001,0.015)$

b)

$log(\frac{P_5}{P_0})=r_5(5)=5\times r_1\sim N(0.005,5\times0.015^2)$

$P(P_5<990)=P(r_5(5)<log(0.99))=0.33\qquad R:pnorm(log(0.99),0.005,sqrt(5)*0.015)$

###Quetion_6:

a)

$r_t(4)\sim N(4\times 0.06,4\times 0.47)$

b)

$P(r_t(4)<2)=0.90\qquad R:pnorm(2,4*0.06,sqrt(4*0.47))$

c)

0.47

d)

$N(0.72,2*0.47)$

###Quetion_7:

a)

$log(\frac{X_2}{X_0})=r_2(2)=r_1+r_2\sim N(2\mu,2\sigma^2))$

$P(X_2>1.3X_0)=P(\frac{X_2}{X_0}>1.3)=P(r_2(2)>log(1.3))$

b)

$\frac{1}{x\sigma \sqrt{2\pi}}exp\{-\frac{log(x)-\mu -log(X_0)}{2\sigma^2}\}$

c)

$X_0exp\{Q_{0.9}\}=X_0exp\{z_{0.9}\sqrt{k}\sigma+k\mu\}$

e)

Sharp-ratio for $r_k:\frac{\mu}{\sigma}$

Sharp-ratio for $log(X_k)-log(X_0):\frac{\sqrt{k}\mu}{\sigma}$

###Quetion_8:

$P'=1500\times (1+\frac{0.043}{0.5})^{0.5\times 6}\approx1921.24$

###Quetion_9:

###Quetion_10:

```{r}
library(tseries)
library(timeSeries)
DJIA = get.hist.quote(instrument = "DJI",
                      start="2016-01-01",end="2016-12-31",
                      quote = c("AdjClose"),
                      provider = "yahoo", 
                      compression = "d")
log_ruturn = diff(log(DJIA))
mu = mean(log_ruturn)
std = sd(log_ruturn)
SR = mu/std
n = 250
c(SR - 1.96 * sqrt((1 + SR^2/2)/n), SR + 1.96 * sqrt((1 + SR^2/2)/n))
```







