---
title: "Tut8_ST5218"
author: 
- Name:Zhu Xu
- User ID:E0337988
- Matriculation ID:A0191344H
date: "9/April/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\rule[-5pt]{16.3cm}{0.15em}
\linespread{1.3}

###Question 1:

####a)
\begin{center}
$\gamma(0)=(1+1.2^2+0.3^2)$

$\gamma(1)=1\times1.2+1.2\times(-0.3)$

$\gamma(2)=1\times(-0.3)$

$\gamma(3)=\gamma(4)=\gamma(5)=0$
\end{center}
Thus

$$
\rho(1)=0.332,\rho(2)=-0.119,\rho(3)=\rho(4)=\rho(5)=0
$$

####b)

We have

$$
\gamma(0)=0.5\gamma(1)+1,\quad\gamma(1)=0.5\gamma(0),\quad\gamma(h)=0.5\gamma(h-1)\quad for\quad h>1
$$

Thus

$$
\rho(h)=0.5^h\quad for\quad h\geq 1
$$

####c)

Similarly

$$
\gamma(0)=\frac{1}{1-0.098^2};\qquad\gamma(1)=\frac{0.98}{1-0.98^2};\qquad\rho(h)=0.98^h,\quad h\geq 1
$$

\newpage
####d)

Fram $Z_t-1.3Z_{t-1}+0.4Z_{t-2}=a_t$, we have
\begin{center}
$\gamma(0)-1.3\gamma(1)+0.4\gamma(2)=4$

$\gamma(1)-1.3\gamma(0)+0.4\gamma(1)=0$

$\gamma(2)-1.3\gamma(1)+0.4\gamma(0)=0$

$\gamma(h)-1.3\gamma(h-1)+0.4\gamma(h-2)=0$
\end{center}
Then

$$
\gamma(0)=34.5679,\quad\gamma(1)=32.0988,\quad\gamma(2)=27.9012,\quad\gamma(h)=1.3\gamma(h-1)-0.4\gamma(h-2)
$$

Thus we have 
\begin{center}
$\gamma(3)=1.3\times27.9012-0.4\times32.0988=23.4320$

$\gamma(4)=1.3\times23.4320-0.4\times27.9012=19.3011$

$\gamma(5)=1.3\times19.3011-0.4\times23.4320=15.7186$
\end{center}
###Question 2:

Since
\begin{center}
$y_{t+1|t}=\mu+\phi_1(y_t-\mu)$

$y_{t+2|t}=\mu+\phi_1(y_{t+1|t}-\mu)=\mu+\phi_1^2(y_t-\mu)$

$y_{t+3|t}=\mu+\phi_1(y_{t+2|t}-\mu)=\mu+\phi_1^3(y_t-\mu)$

$y_{t+h|t}=\mu+\phi_1(y_{t+h-1|t}-\mu)=\mu+\phi_1^h(y_t-\mu)\rightarrow\mu$ as $h\rightarrow\infty$
\end{center}
Thus write the model as

$$
Y_t=\mu+\phi_1(Y_{t-1}-\mu)+a_t
$$

###Question 3:

After $q+1$ steps.

###Question 4:
\begin{align*}
y_t&=a_t+\theta_1 a_{t-1}\\
&=a_t+\theta_1(\theta_1 a_{t-2}+a_{t-1})\\
&=a_t+\theta_1 a_{t-1}+\theta_1^2 a_{t-2}\\
&=\cdots\\
&=a_t+\theta_1 a_{t-1}+\cdots+\theta_1^{h-1}a_{t-h+1}+\theta_1^h a_{t-h}\\
&\rightarrow AR(\infty)
\end{align*}

\newpage
###Question 5:

####a)

```{r}
library(tseries)
library(timeSeries)
P = get.hist.quote(instrument ='GOOG',start='2001-01-01',
                   end='2014-12-31', quote=c('AdjClose'),
                   provider='yahoo', compression='d')
plot(P, type='l')
```

####b)

```{r}
r = diff(P)
plot(r)
```

####c)

```{r}
model1 = arima(P, order=c(1, 1, 1))
tsdiag(model1)
model2 = arima(P, order=c(2, 1, 1))
tsdiag(model2)
model3 = arima(P, order=c(2, 1, 2))
tsdiag(model3)
```


###Question 6:

####a)

$$
E_{y_t}=2+0.7E_{y_{t-1}}+Ea_t+0.3Ea_{a-1}+0.4Ea_{t-2}=2+0.7E_{y_{t-1}}
$$

By its being stationary,$E_{y_{t-1}}=E{y_{t}}$, thus

$$
E_{y_t}=2+0.7E_{y_{t}}=\frac{2}{1-0.7}=\frac{20}{3}
$$

####b)

$$
a_{t-1}=y_{t-1}-y_{t-1|t-2}=1-\frac{20}{3}=-5.667
$$

Then we predict

$$
y_t=2+0.7\times1+0+0.3\times(-5.667)+0.4\times0=0.999
$$

####c)

$y_{y-1}=1$

$$
a_{t-2}=y_{t-2}-y_{t-2|t-3}=0.5-\frac{20}{3}=-6.1667
$$

Then

$$
y_{t-1|t-2}=2+0.7\times0.5+0+0.3\times(-6.1667)+0.4\times0=0.4999
$$

$$
a_{t-1}=y_{t-1}-y_{t-1|t-2}=1-0.4999=0.5001
$$

Thus

$$
y_t=2+0.7\times1+0+0.3\times0.5001+0.4\times(-6.1667)=0.3833
$$
