---
title: "ST5201-Homework5"
author: 
- Zhu Xu 
- User ID:E0337988
- Student ID:A0191344H
date: "2018/11/15"
output: 
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\noindent\rule[-5pt]{16.3cm}{0.15em}
\linespread{1.5}

###Q1：

####a)

```{r warning = FALSE}
T=rep(0,500)
for(i in 1:500){
x=rnorm(7,5,5)
T[i]=(mean(x)-5)/sqrt(var(x)/7)
}
p1 = hist(T,breaks=20,plot = F)
p2 = hist(T,breaks=50,plot = F)
p3 = hist(T,breaks=100,plot = F)
plot(p1,col = "pink",main="p-value")
plot(p2,col = "lightgreen",add = T)
plot(p3,col = "lightblue",add = T)
```

\newpage

####b)

```{r}
d1=density(T,bw =0.025)
d2=density(T,bw =0.125)
d3=density(T,bw =1.25)
plot(d1, lwd = 2,col="pink",main="kernel density",xlab="")
lines(d2, lwd = 2,col = "lightgreen")
lines(d3, lwd = 2,col = "lightblue")
legend('topright',
       legend,c("bandwith=0.025","bandwith=0.125","bandwith=1.25"),
       col=c("skyblue","pink","grey"),
       pch=1,lwd = 1,inset=0.01)
```

\newpage

####c)

```{r}
qqnorm(T,main = "T distribution Q-Q Plot",xlab = "Theoretical Quantiles", ylab = "Sample Quantiles",plot.it = TRUE)
qqline(rt(500, df = 6), col = 2, pch=21)
```

\newpage

###Q2:

####a)

```{r}
Q2=read.table(
  "/Users/xuzhu/Desktop/Notes/ST5201/Homework/hw5/Q2.txt")
x=Q2[,2]
boxplot(x,main="Boxplot",ylab="Q2")
```

####b)

```{r}
stem(x)
```

####c)

```{r}
mean(x)
median(x)
```

###Q3:

####a)
\begin{center}
$\mu = 140$
\end{center}
\begin{center}
$\{\bar{X}\geq\mu-t_{n-1}(\frac{a}{2})\frac{S}{n}\}\cup\{\bar{X}\leq\mu + t_{n-1}(\frac{a}{2})\frac{S}{n}\}$
\end{center}

####b)

```{r}
t.test(x,mu=140)
```

\newpage

####c)

```{r}
confint<-function(x,alpha=0.10)
{
  n=length(x)
  xb=mean(x)
  sigma=sqrt(n/(n-1))*sd(x)
  tmp=sd(x)/sqrt(n)*qt(1-alpha/2,n-1)
  df= n-1
  data.frame(mean=xb,df=df,a=xb-tmp,b=xb+tmp)
}
confint(x)
```

####d)

```{r}
confint2<-function(x,alpha=0.10)
{
  n=length(x)
  xb=mean(x)
  sigma2=var(x)
  a=n*sigma2/qchisq(alpha/2,n-1)
  b=n*sigma2/qchisq(1-alpha/2,n-1)
  df=n-1
  data.frame(sigma2=var(x),df=df,a,b)
}
confint2(x)
```

\newpage

###Q4:

####a)

\begin{center}
$z_1=X;\quad z_2=X+Y\qquad\Rightarrow |J^{-1}|=1,\quad X=z_1,\quad Y=z_2 - z_1$\\
$f(x,y)=\frac{1}{2\pi}exp\{-\frac{x^2+y^2}{2}\}$
\end{center}
\begin{align*}
f_{z_1,z_2}(z_1,z_2)&=|J^{-1}|f_{X,Y}(z_1.z_2)\\
&=\frac{1}{2\pi}exp\{-\frac{1}{2}[z_1^2 + (z_2 - z_1)^2]\}\\
&=\frac{1}{2\pi}exp\{-\frac{1}{2}(2z_1^2 + z_2^2 - 2z_1 z_2)\}\\
\end{align*}
\begin{align*}
f(x,x+y)&=\frac{1}{2\pi}exp\{-\frac{1}{2}[2x^2 + (x+y)^2 - 2x(x+y)]\}\\
&=\frac{1}{2\pi}exp\{-\frac{x^2+y^2}{2}\}
\end{align*}

####b)

\begin{align*}
&f(x)=\frac{1}{\sqrt{2\pi}}e^{-\frac{x^2}{2}}\\
&f(x+y)=\frac{1}{2\sqrt{\pi}}e^{-\frac{1}{4}(x+y)^2}\\
&f(x)f(x+y)=\frac{1}{2\sqrt{2}\pi}exp\{-\frac{x^2+\frac{1}{2}(x+y)^2}{2}\}\neq f(x,x+y)
\end{align*}
\begin{center}
Thus X and X+Y are not independent.
\end{center}

####c)

\begin{center}
$z_3=X-Y;\quad z_4=X+Y\qquad\Rightarrow |J^{-1}|=\frac{1}{2},\quad X=\frac{z_3+z_4}{2},\quad Y=\frac{z_4 - z_3}{2}$
\end{center}
\begin{center}
$f_{Z_3,Z_4}(z_3,z_4)=|J^{-1}|f_{X,Y}(z_3,z_4)=\frac{1}{4\pi}exp\{-\frac{z_3^2+z_4^2}{4}\}$
\end{center}
\begin{center}
$f(x-y,x+y)=\frac{1}{4\pi}exp\{-\frac{1}{4}[(x-y)^2+(x+y)^2]\}$
\end{center}

####d)

\begin{center}
$f(x-y)=\frac{1}{2\sqrt\pi}exp\{-\frac{(x-y)^2}{4}\}$
\end{center}
\begin{center}
$f(x-y)f(x+y)=\frac{1}{4\pi}exp\{-\frac{(x-y)^2}{4}\}exp\{-\frac{(x+y)^2}{4}\}=f(x-y,x+y)$
\end{center}
\begin{center}
Thus $X+Y$ and $X-Y$ are independent.
\end{center}

