---
title: "ST5210-Tut4"
author: "Name:Zhu Xu<br>User ID:E0337988<br>Student ID:A0191344H"
date: "18 Spetember 2018"
output:
  html_document:
    df_print: paged
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 1:

```{r}
library(tseries)
##(a)
dji <- get.hist.quote(instrument = "^DJI", start="2000-01-01",
                     quote = c("AdjClose"),provider = "yahoo", compression = "d")
##(b)
returns <- diff(log(dji)) 

##(c)
Tue <- (weekdays(time(returns))== "???ڶ?" )
##(d)
Tue_adj <- returns[Tue] 
Mon <- ( weekdays(time(returns)) == "????һ" )
Wed <- ( weekdays(time(returns)) == "??????" )
Thu <- ( weekdays(time(returns)) == "??????" )
Fri <- ( weekdays(time(returns)) == "??????" )

Mon_adj <- returns[Mon]
Wed_adj <- returns[Wed]
Thu_adj <- returns[Thu]
Fri_adj <- returns[Fri]

t.test(Tue_adj, Mon_adj)
t.test(Tue_adj, Wed_adj)
t.test(Tue_adj, Thu_adj)
t.test(Tue_adj, Fri_adj)

##(e)
t.test(Tue,Mon, paired = T)
t.test(Tue,Wed, paired = T)
t.test(Tue,Thu, paired = T)
t.test(Tue,Fri, paired = T)

```

# Question 2:

```{r}
Data <- read.csv("C:/Users/MSI/Desktop/Notes/ST5210-Multivariate Data Analysis/Tutorial/Tutorial04/dailyReturn.csv", header = T)
portfolios <- Data[,-1]
colnum <- ncol(portfolios)
test.data <- portfolios[,c(2:colnum)] - portfolios[,c(1:colnum-1)]
library(mvtnorm)
library(ICS)
library(ICSNP)
HotellingsT2(test.data)
```


\usepackage{amsmath}

#Question 3:

###a)

\begin{align*}
&\qquad Var(\bar{X})=E(\bar{X})^2-[E(\bar{X})]^2\\
&\Rightarrow \frac{1}{n^2}Var(\sum_{i=1}^{n}X_i)=[E(\bar{X})]^2-[\frac{1}{n}E(\sum_{i=1}^{n}X_i)]^2\\
&\Rightarrow \frac{\sum_x}{n}=E(\bar{X})^2-\mu_{X}^{2}\\
&\Rightarrow E(\bar{X})^2=\frac{\sum_x}{n}+\mu_{X}^{2}\\
&\Rightarrow E(\bar{Y})^2=\frac{\sum_y}{n}+\mu_{Y}^{2}\\
\end{align*}

\begin{align*}
\qquad E[(\bar{X}-\bar{Y})^2]&=E[\bar{X}^2+\bar{Y}^2-2\bar{X}\bar{Y}]\\
&=E(\bar{X}^2)+E(\bar{Y}^2)-2EE(\bar{X}\bar{Y})\\
&=\frac{\sum_x}{n}+\mu_{X}^2+\frac{\sum_y}{n}+\mu_y^2-2\mu_X\mu_Y\\
[E(\bar{X}-\bar{Y})]^2&=[E(\bar{X}-E(\bar{Y})]^2\\
&=\mu_{x}^2+\mu_{y}^2-2\mu_{x}\mu_{Y}\\
Var(\bar{X}-\bar{Y})&=E[(\bar{X}-\bar{Y})^2]-[E(\bar{X}-\bar{Y})]^2\\
&=\frac{\sum_x}{n}+\mu_{X}^2+\frac{\sum_y}{n}+\mu_y^2-2\mu_X\mu_Y-\mu_{x}^2-\mu_{y}^2+2\mu_{x}\mu_{Y}\\
&=\frac{\sum_x}{n}+\frac{\sum_y}{n}
\end{align*}

###b)

\begin{align*}
Var(\bar{X})&=\frac{\sum_x}{n};\qquad Var(\bar{Y})=\frac{\sum_y}{n}\\
2cov(\bar{X},\bar{Y})&=2cov(\frac{\sum_{i=1}^{n}X}{n},\frac{\sum_{i=1}^{n}Y}{n})\\
&=\frac{2}{n^2}cov(X_1+\cdots +X_n,Y_1+\cdots +Y_n)\\
&=\frac{2}{n^2}[cov(X_1,Y_1)+\cdots +cov(X_n,Y_n)]\\
&=\frac{2n\sum_{XY}}{n^2}\\
&=\frac{2\sum_{XY}}{n}
\end{align*}

#Question 4:

$\qquad D\sim N(A\mu,A\sum A^{T})$
$$
A=
\begin{bmatrix}
1&-1&0\\
0&1&-1\\
\end{bmatrix}
$$

$$
A_\mu=\begin{bmatrix}
1&-1&0\\
0&1&-1\end{bmatrix}
\begin{bmatrix}
\mu_1\\
\mu_2\\
\mu_3\end{bmatrix}
=\begin{bmatrix}
\mu_1-\mu_2\\
\mu_2-\mu_3\end{bmatrix}
$$


$$
\begin{align*}
A\sum A^{T}&=\begin{bmatrix}
1&-1&0\\
0&1&-1\end{bmatrix}
\begin{bmatrix}
\sigma_{11}&\sigma_{12}&\sigma_{13}\\
\sigma_{21}&\sigma_{22}&\sigma_{23}\\
\sigma_{31}&\sigma_{32}&\sigma_{33}\end{bmatrix}
\begin{bmatrix}
1&0\\
-1&1\\
0&-1\end{bmatrix}\\
&=\begin{bmatrix}
\sigma_{11}-\sigma_{21}&\sigma_{12}-\sigma_{22}&\sigma_{13}-\sigma_{23}\\
\sigma_{21}-\sigma_{31}&\sigma_{22}-\sigma_{32}&\sigma_{23}-\sigma_{33}\end{bmatrix}
\begin{bmatrix}
1&0\\
-1&1\\
0&-1\end{bmatrix}\\
&=\begin{bmatrix}
\sigma_{11}-\sigma_{21}-\sigma_{12}+\sigma_{22}&\sigma_{12}-\sigma_{22}-\sigma_{13}+\sigma_{23}\\
\sigma_{21}-\sigma_{31}-\sigma_{22}+\sigma_{32}&\sigma_{22}-\sigma_{32}-\sigma_{23}+\sigma_{33}\end{bmatrix}\\
&=\begin{bmatrix}
\sigma_{11}-2\sigma_{21}+\sigma_{22}&\sigma_{12}-\sigma_{22}-\sigma_{13}+\sigma_{23}\\
\sigma_{21}-\sigma_{31}-\sigma_{22}+\sigma_{32}&\sigma_{22}-2\sigma_{32}+\sigma_{33}\end{bmatrix}
\end{align*}
$$



